Spatial Reasoning and Data Displays

### 2015-01-09 Paper/Draft1/TestingVisualAptitude.Rnw
no reversal anymore

This aspect of lineups provides an important tool in the evaluation of graphical findings. However, the testing situation can be reversed, and lineups allow for an objective evaluation of an individual's visual ability based on the general's population performance on a lineup.

>>>>

This aspect of lineups provides an important tool in the evaluation of graphical findings. Similarly, lineups allow for an objective evaluation of an individual's visual ability based on the general's population performance on a lineup.
